% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[11pt]{res}
\topmargin=-0.280in  % start text higher on the page
\setlength{\textheight}{9.75in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings
\begin{document}  
\name{Andrew Schechtman-Rook}

\address{rook166@gmail.com --- (917)-836-4267}
                        
\begin{resume} 
\vspace{-0.1in}
\section{\centerline{\large SUMMARY}}
\vspace*{0.15 in}\begin{itemize}\itemsep -2pt
\addtolength{\itemindent}{-0.215in}
%\centering
\item 8+ years of experience with analysis of large, complex datasets.
\item Strong programming, numerical analysis, and visualization skills.
\item Extensive familiarity with linear and non-linear model fitting.
\item Experience writing software for both parallel and distributed
  environments.
\item Able to work independently as well as part of a team.
\item Practiced writer and speaker for technical and non-technical
  audiences.
\end{itemize}
\vspace{-0.1in}
\section{\centerline{\large SKILLS}}
                    {\bf Programming:} C++, Python (including
                    Matplotlib, Numpy, Scikit-learn, Scipy), shell scripting.\\
                      {\bf Databases and Web Design:} Django, HTML, MySQL, PHP.\\
                        {\bf Operating Systems:} Linux, Mac OS X.\\
                        {\bf Data Analysis:} Bootstrapping; genetic algorithms; image
                        processing and machine vision; interpolation;
                        linear and non-linear regression; Monte Carlo; numerical integration and
                        differentiation; parallel and distributed
                        computing; principal component analysis; rootfinding.\\
                     {\bf Oral Presentations:} Described advanced
                       analysis and modeling to both expert and
                       non-expert audiences through engaging lectures
                       and informal discussions.\\
                       {\bf Writing:} Published research in leading
                         scientific journals (full list
                         available upon request). 
\vspace{-0.1in}
\section{\centerline{\large PROFESSIONAL EXPERIENCE}}
{\bf Postdoctoral Research Associate}\hfill\mbox{2014-Present}\\
University of Wisconsin-Madison
                  \vspace* {0.01 in}\begin{itemize} \itemsep -2pt
                    %\addtolength{\itemindent}{-0.215in}
                    \item Devised metrics to improve correspondence between numerical models and
                      astronomical data. Implemented in highly
                      optimized Python, was able to refine agreement by
                      up to 20\% with minimal increase in computation time.
                    \item Built a fast Voronoi Tesselation algorithm
                      to adaptively bin images, preserving spatial
                      resolution while maximizing signal over images
                      with over one million pixels.
                    \item Constructed visualization tools using
                      Matplotlib to
                      aid data processing efforts.
                    \item Trained and mentored undergraduate and
                      graduate students in programming, data analysis and statistical methods.
                    \end{itemize}
\vspace{-0.15in}
{\bf Research Assistant}\hfill\mbox{2007-2013}\\
University of Wisconsin-Madison
                  \vspace* {0.01 in}\begin{itemize} \itemsep -2pt
                    %\addtolength{\itemindent}{-0.215in}
                    \item Developed non-linear Levenberg-Marquardt
                      $\chi^{2}$ fitting algorithms using a
                      combination of Python and C++ to constrain
                      models of spiral galaxies to data. 
                   \item Employed on-campus distributed computing
                     resources to perform large-scale modeling in parallel, using over 20 years of computer time
                     in 1 month.
                   \item Assembled a hybrid C++/Python processing
                     pipeline to clean, register, and
                     mosaic hundreds of high-resolution images with
                     minimal user intervention, resulting in a factor
                     of 10+ increase in analysis precision.
                   \item Created a genetic
                     algorithm in C++ to efficiently fit galaxy models with
                     unusually large numbers of
                     free parameters to high-resolution images.
                   \item Utilized frequency-domain analysis to
                     understand the spatial distribution of galactic structure.
                  \item Computed descriptive statistics about
                    200+ astronomical objects from raw survey data
                    automatically via custom-built analysis software
                    blending C++ and shell scripting programs.
                  \item Implemented methods comparing different
                    fitting statistics to compute global best-fitting
                    parameters for multiple datasets. 
                  \item Discovered and classified a previously unknown
                    galaxy by simultaneously using data from seven different sources. 
                  \end{itemize} 
\vspace {-0.15 in}
{\bf Teaching Assistant}\hfill\mbox{2008-2009}\\
University of Wisconsin-Madison
\vspace*{0.01 in}\begin{itemize}\itemsep -2pt
  %\addtolength{\itemindent}{-0.215in}
\item Taught six discussion sections of an introductory undergraduate
  astronomy course.
\item Prepared engaging lesson plans, including interactive demonstrations and
  group problem-solving activities.
\end{itemize}
\vspace{-0.15 in}
{\bf Research Assistant}\hfill\mbox{2006-2007}\\
Case Western Reserve University
                  \vspace* {0.01 in}\begin{itemize} \itemsep -2pt
                    %\addtolength{\itemindent}{-0.215in}
                    \item Designed and executed statistical analyses
                      of simulated galaxy clusters to optimize
                      strategy for future data acquisition.
                    \item Used nearest-neighbor and
                      regression analysis to compute a transform
                      between astronomical filter systems. 
                  \end{itemize} 
\vspace {-0.15 in}
{\bf Physics Lab Assistant}\hfill\mbox{2005-2006}\\
Case Western Reserve University
\vspace*{0.01 in}\begin{itemize} \itemsep -2pt
  %\addtolength{\itemindent}{-0.215in}
\item Maintained existing equipment and computers for introductory
  physics labs.
\item Developed and built components for new labs.
\item Upgraded hardware and software for over 20 lab computers.
\end{itemize}
\vspace{-0.1in}
\section{\centerline{\large OTHER RELEVANT EXPERIENCE}}
{\bf Independent NFL Analyst}\hfill\mbox{2013-Present}\\
phdfootball.blogspot.com
                  \vspace* {0.01 in}\begin{itemize} \itemsep -2pt
                    %\addtolength{\itemindent}{-0.215in}
                    \item Performed novel statistical analyses on
                      publicly available NFL data.
                    \item Mined a play-by-play database containing
                      over 500,000 records across dozens of tables
                      for complex relationships between individual players
                      as well as teams. 
                    \item Developed custom software and visualization
                      tools using MySQL and Python to efficiently examine thousands of plays. 
                    \item Explained findings in a manner accessible to all audiences through both written posts and evocative figures.
                  \end{itemize} 
\vspace{-0.1 in}

\section{\centerline{\large EDUCATION}}
Ph.D., Astronomy, University of Wisconsin-Madison \hfill\mbox{December 2013}
\begin{itemize} \itemsep -2pt
\item Wisconsin Space Grant Consortium Graduate Fellowship
\item International Astronomical Union Travel Grant
\item American Astronomical Society Chambliss Student Award
\item University of Wisconsin-Madison Astronomy Department Whitford Award
\end{itemize}
\vspace{-0.15 in}
MS, Astronomy, University of Wisconsin-Madison \hfill\mbox{June 2009}\\
BS, Astronomy, Case Western Reserve University \hfill\mbox{May 2007} 
\begin{itemize} \itemsep -2pt
\item Graduated {\it cum laude}
\item Minors in Physics and Classics
\end{itemize}
% \vspace{-0.1in}
% \section{\centerline{\large SELECTED PUBLICATIONS}}
% {\bf Schechtman-Rook, A.} \& Bershady, M. A., ``Near-Infrared Structure
% of Fast and Slow Rotating Disk Galaxies'', 2014, {\it in prep}\\
% {\bf Schechtman-Rook, A.}, Ph.D. Dissertation: ``Lifting the Dusty
% Veil: Understanding the Stellar Structure of Spiral Disks'', 2013\\
% {\bf Schechtman-Rook, A.} \& Bershady, M. A., ``Near-infrared Detection
% of a Super-thin Disk in NGC 891'', 2013, {\it ApJ}, 773, 45\\
% {\bf Schechtman-Rook, A.} \& Hess, K. M., ``NGC 4656UV: A UV-selected
% Tidal Dwarf Galaxy Candidate'', 2012, {\it ApJ}, 750, 171\\
% {\bf Schechtman-Rook, A.}, Bershady, M. A., \& Wood, K., ``The
% Three-dimensional Distribution of Dust in NGC 891'', 2012, {\it ApJ}, 746,70

 
\end{resume} 
\end{document}









