% LaTeX file for resume 
% This file uses the resume document class (res.cls)
\documentclass[11pt]{res}
\usepackage{hyperref}
%\hypersetup{
%    colorlinks=true,
%    linkcolor=blue,
%    %filecolor=magenta,      
%    urlcolor=blue,
%}
\topmargin=-0.380in  % start text higher on the page
\setlength{\textheight}{9.75in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings
\begin{document}  
\name{Andrew Schechtman-Rook}

\address{rook166@gmail.com\\(917)-836-4267}
\address{\url{https://github.com/AndrewRook}}
                        
\begin{resume} 
\vspace{-0.1in}
\section{\centerline{\large EDUCATION}}
Ph.D., Astronomy, University of Wisconsin-Madison \hfill\mbox{December 2013}\\
MS, Astronomy, University of Wisconsin-Madison \hfill\mbox{June 2009}\\
BS, Astronomy, Case Western Reserve University \hfill\mbox{May 2007}\\
\vspace{-0.3in}
\section{\centerline{\large EXPERIENCE}}
{\bf Manager, Data Science}\hfill\mbox{2016-present}\\
Capital One
\vspace*{0.01 in}\begin{itemize} \itemsep -2pt
  \item Created a Python library to facilitate the creation and
    refinement of robust, production-ready data analysis pipelines,
    saving hundreds of hours of R\&D effort.
  \item Led development of a proof-of-concept automated machine learning model
    deployment scheme for cloud-based applications, and helped
    multiple teams implement the system in their own projects.
  \item Constructed a model to predict customer credit-card spend
    based on application information 25\% better than existing design,
    and advised leadership on its value and proper use.
\end{itemize}
\vspace{-0.15in}

{\bf Principal Data Scientist}\hfill\mbox{2014-2016}\\
Capital One Labs
\vspace*{0.01 in}\begin{itemize} \itemsep -2pt
  \item Built and deployed an interactive course completion dashboard using Flask
    and dc.js to provide progress reports to individual students as
    well as company leadership.
  \item Implemented a novel approach to deliver internal technical
    trainings, providing over 5000 hours of classes with no instructors.
  \item Engineered a credit card payment simulator, allowing a product team
    to gain actionable insights without expensive pilot programs.
  \end{itemize}
\vspace{-0.15in}

{\bf Data Science Fellow}\hfill\mbox{2014}\\
The Data Incubator
                  \vspace* {0.01 in}\begin{itemize} \itemsep -2pt
                    \item Trained a model on
                      historical airline on-time arrival data to predict flight
                      delay times.
                    \item Designed a web interface to provide interactive itinerary
                      input and visualizations to intuitively
                      display model results.
                    \end{itemize}
\vspace{-0.15in}

%{\bf Postdoctoral Research Associate}\hfill\mbox{2014}\\
%University of Wisconsin-Madison
%                  \vspace* {0.01 in}\begin{itemize} \itemsep -2pt
%                    \item Improved agreement between numerical models
%                      and astronomical data by 20\%, using vectorized
%                      numpy operations and specialized libraries to
%                      preserve run time.
%                    \item Authored a fast Voronoi Tessellation algorithm
%                      to adaptively bin images, preserving spatial
%                      resolution while maximizing signal in images
%                      with over one million pixels.
%                    \end{itemize}
%\vspace{-0.15in}
{\bf Independent NFL Analyst}\hfill\mbox{2013-Present}\\
phdfootball.blogspot.com
                  \vspace* {0.01 in}\begin{itemize} \itemsep -2pt
                    \item Designed a responsive web-based dashboard
                      allowing users to visually filter 350,000
                      plays to identify and explore
                      interesting game situations.
                    \item Authored a Python library to compute
                      play-by-play win probabilities based on game situation.
                    \item Developed a program to automatically remove
                      camera motion from NFL game footage. 
%                    \item Mined a play-by-play database containing
%                      over 500,000 records across dozens of tables
%                      for deep relationships between individual players
%                      as well as teams. 
%                    \item Explained findings to a broad audience through both written posts and evocative figures.
                  \end{itemize} 
\vspace{-0.15in}
{\bf Graduate and Postdoctoral Researcher}\hfill\mbox{2007-2014}\\
University of Wisconsin-Madison
                  \vspace* {0.01 in}\begin{itemize} \itemsep -2pt
%                    \item Improved agreement between numerical models
%                      and astronomical data by 20\%, using vectorized
%                      numpy operations and specialized libraries to
%                      preserve run time.
                    \item Devised a fast Voronoi Tessellation
                      algorithm in Python
                      to adaptively bin images, preserving spatial
                      resolution while maximizing signal in images
                      with over one million pixels.
%                   \item Employed on-campus distributed computing
%                     resources to perform large-scale modeling in parallel, using over 20 years of computer time
%                     in 1 month.
                   \item Assembled a hybrid C++/Python processing
                     pipeline to process hundreds of high-resolution images with
                     minimal user intervention, resulting in a 10x increase in analysis precision.
                   \item Created a genetic
                     algorithm in C++ to efficiently fit complex galaxy models to high-resolution images.
                  \item Computed descriptive statistics about
                    200+ astronomical objects from raw survey data
                    automatically via custom-built analysis software
                    blending C++ and shell scripts.
                  \end{itemize} 
\vspace{-0.1in}
\section{\centerline{\large SKILLS}}
                    {\bf Programming:} Python, shell scripting, C++, Javascript.\\
                      {\bf Databases and Web Design:} Flask/Django,
                      MySQL/PostgreSQL, Hive/Beeline.\\
                      {\bf Cloud Computing:} AWS (EC2, ECS, S3,
                      Cloudformation), Ansible.
                        {\bf Operating Systems:} Linux, Mac OS X.\\
                        {\bf Data Analysis:} Parallel and distributed
                        computing, machine
                        learning, spatial analysis, image processing, machine vision.

 
\end{resume} 
\end{document}









